% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Custom LaTeX preamble for font override
\usepackage{fontspec}
\setmainfont{MesloLGL Nerd Font}
\setsansfont{TeX Gyre Heros}
\setmonofont{Courier}
\setmathfont{MesloLGL Nerd Font}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\author{}
\date{}

\begin{document}

\hypertarget{week-1-slides-introduction-to-linear-algebra}{%
	\section{Week 1 Slides: Introduction to Linear
	  Algebra}\label{week-1-slides-introduction-to-linear-algebra}}

\hypertarget{slide-1-linear-algebra-overview}{%
	\subsection{Slide 1: Linear Algebra
		Overview}\label{slide-1-linear-algebra-overview}}

\begin{itemize}
	\tightlist
	\item
	      Linear algebra is the mathematics of vectors and matrices.
	\item
	      Applications in physics, engineering, data science, and ML.
	\item
	      Reference Video:
	      \href{https://www.youtube.com/watch?v=ZK3O402wf1c}{MIT OCW: Vectors
		      and Spaces}.
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{slide-2-vectors}{%
	\subsection{Slide 2: Vectors}\label{slide-2-vectors}}

\begin{itemize}
	\tightlist
	\item
	      Scalars: A single number.
	\item
	      Vectors: A list of numbers.
	\item
	      Example: A 2D vector can be \([x, y]\).
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{slide-3-vector-operations}{%
	\subsection{Slide 3: Vector
		Operations}\label{slide-3-vector-operations}}

\begin{itemize}
	\tightlist
	\item
	      Addition: {[}\mathbf{u} + \mathbf{v}
	      \rightarrow \text{Tip-to-Tail Rule.}{]}
	\item
	      Scalar Multiplication: {[}c\cdot \mathbf{v}
	      \rightarrow \text{Scaling vector magnitude.}{]}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{slide-4-dot-product}{%
	\subsection{Slide 4: Dot Product}\label{slide-4-dot-product}}

\begin{itemize}
	\tightlist
	\item
	      Formula: {[}\mathbf{u} \cdot \mathbf{v} =
	      \textbar{}\mathbf{u}\textbar{} \textbar{}\mathbf{v}\textbar{}
	      \cos\theta{]}
	\item
	      Applications:

	      \begin{itemize}
		      \tightlist
		      \item
		            Angle calculations.
		      \item
		            Projections.
	      \end{itemize}
\end{itemize}

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

\hypertarget{slide-5-practice}{%
	\subsection{Slide 5: Practice}\label{slide-5-practice}}

\begin{enumerate}
	\def\labelenumi{\arabic{enumi}.}
	\tightlist
	\item
	      Compute the dot product of ({[}1, 2{]}) and ({[}3, 4{]}).
	\item
	      Visualize vector addition for ({[}3,4{]}) and ({[}5,2{]}).
	\item
	      Write SageMath code for \(\| \mathbf{v} \|\).
\end{enumerate}

\end{document}
